This chapter focuses on providing the basis for all following theorems and proofs by displaying most of the definitions regularly used in this thesis. I collected and structured them starting with the simple ones and advancing to more complex and specific concepts. This should give an overview and a better understanding of the methods we will use later on.\\

We will start with defining the concept of a graph. For a set $X$, let us denote the set of all $2$-element subsets of $X$ with ${X\choose 2} =\lbrace \lbrace x,y\rbrace : x,y\in V, x\neq y\rbrace$.
\begin{defn}[Graph]
A \textit{graph} $G$ is a tuple $G=(V,E)$, where $V=V(G)$ denotes the set of vertices and $E=E(G)\subseteq {V\choose 2}$ is the set of edges. Here, each edge is a set of two vertices from $V$.
\end{defn}

By giving each edge a direction, i.e. saying the edge $(x,y)$ points from $x$ to $y$, we create a \textit{directed graph} $D=(V,E)$ where $V$ again denotes the set of vertices but $E\subseteq \lbrace (x,y) : x,y\in V, x\neq y\rbrace$ is now a set of tuples. In a directed graph, there can exist two edges between two vertices $x$ and $y$: one pointing to $x$ and one pointing to $y$. If there exists at most one edge for any pair of vertices in a directed graph $D$, we call $D$ also an \textit{oriented graph}.

\begin{note}
Note that any of the following concepts and definitions can be applied to directed graphs as well.
\end{note}

If two vertices are neighbors in a graph $G=(V,E)$, i.e. there exists an edge between them, they are \textit{adjacent} to each other. Then, the edge and the vertices are called \textit{incident} to each other. We denote the neighbors of a vertex $v\in V$ in $G$ as $N_G(v)$ or just $N(v)$ if there is no confusion in regard of the underlying graph. Furthermore, we say $v$ is of \textit{degree} $\delta (v) =\vert N(v)\vert$. The maximum degree in a graph is denoted by $\Delta (G)$. Since edges in a directed graph do not necessarily all point in the same direction, there we distinguish between the \textit{in-degree} $\delta^{in}(v)$ of a vertex $v$ which counts the number of edges ending in $v$ and the \textit{out-degree} $\delta^{out}(v)$ which counts the number of edges starting at $v$.\\

After introducing the concept of a graph and the relations between edges and vertices we now start looking for structures of a greater scale in it either by considering just the vertices and edges or later by additionally defining colorings of the graph. 

Let $G=(V,E)$ be a graph. A graph $H=(V^\prime ,E^\prime )$ is a \textit{subgraph} of $G$, written $H\subseteq G$, if $V^\prime\subseteq V$, $E^\prime\subseteq \lbrace \lbrace x,y\rbrace : x,y\in V^\prime, x\neq y\rbrace$ and any edge $e\in E^\prime$ is also in $E$. The graph $H$ is called an \textit{induced subgraph} of $G$ and we write $H\subseteq_I G$ if $E^\prime = E\vert_{V^\prime}$, i.e. for any edge $e=\lbrace x,y\rbrace\in E$ holds: if $x\in V^\prime$ and $y\in V^\prime$, then $e\in E^\prime$. The subgraph induced in $G$ by a certain set of vertices $A\subseteq V$ is denoted as $G[A]$. Furthermore, the structures of two graphs can coincide completely: Two graphs $G$ and $H$ are called \textit{isomorphic} if there exists a bijection $\phi :V(G)\to V(H)$ such that $(\phi (u), \phi (v))\in E(H)$ if and only if $(u, v)\in E(G)$. We denote such a relation as $G\approx H$.

A subset $S\subseteq V$ of pairwise non-adjacent vertices, i.e. $E\vert_S =\emptyset$, is called a \textit{stable} or \textit{independent} set. Opposite to that, a \textit{clique} is a set of vertices $S\subseteq V$ such that all vertices in $S$ are pairwise adjacent. The size of the largest clique in $G$ is denoted by $\omega (G)$. A \textit{coloring} $c$ of $G$ with $r$ colors is a function $c:V\to [r]$ that maps a color to each vertex. It is a proper coloring if $\forall e = \lbrace x,y\rbrace\in E: c(x)\neq c(y)$, i.e. no two adjacent vertices have the same color. Then, we can define the chromatic number $\chi (G)$ of $G$ as the minimum number of colors needed for a proper coloring of $G$. Observe that each color class of a proper coloring, i.e. all vertices of the same color, is a stable set.

A way of obtaining a proper coloring for a graph $G$ that always works is the \textit{greedy coloring}: Order the vertices $v_1, v_2, \dots ,v_{\vert V(G) \vert }$ and define a coloring $c$ by assigning each vertex the first available color, i.e. the first color not used on a neighbor with smaller index. Note that it often is far from optimal regarding the number of used colors.\\

Since the crucial part of this thesis deals with the conjecture of Gyárfás and Sumner, we want to introduce the notion of $\chi$-bounded families of graphs. In addition, this part states the definitions of a hypergraph and the Ramsey number because they are used in many proofs in the following chapters.

\begin{defn}[Bounding function]\label{d1}
A $\chi$\textit{-bounding function} $f:\N\to\N$ for a family $\mathcal{F}$ of graphs is a function such that $\chi (G)\leq f(\omega (G))$ holds for each $G\in\mathcal{F}$. Then, $\mathcal{F}$ is called $\chi$-bounded.
\end{defn}

A \textit{hypergraph} $H=(V,E)$ is a graph where $V$ is a set of vertices and $E$ a set of non-empty subsets of $V$, called hyperedges. If each edge has the same size $s$, $H$ is a $s$-uniform hypergraph. Note that the concepts of colorings also apply for hypergraphs. Here, a coloring $c$ of a hypergraph $H$ is proper if there exists no monochromatic edge, i.e. there is no edge $e\in E(H)$ with $c(v)=\alpha$ for all $v\in e$ and some color $\alpha$.

The Ramsey number $R=R(r_1,\dots ,r_s)$ is the minimum number $R\in\N$, such that for every coloring $c:[R]^2\to [s]$, there exist a color $\alpha\in [s]$ and a subset $X\subseteq [R]$, $\vert X\vert =r_{\alpha}$, with $c(i,j)=\alpha$ for all $(i,j)\in [X]^2$, $i\neq j$.\\

Proving the conjecture as a whole is obviously a complex endeavor. That is why many proofs concentrate on certain graphs and prove it only partially. Therefore, the next definitions are a collection of the most used special graphs or characterizations of some graphs that appear throughout this thesis.


Consider a graph $G=(V,E)$ with $\vert V\vert = n$. If $E=\emptyset$, we call $G$ the empty graph on $n$ vertices. If $E= {V\choose{2}}$, $G$ is also denoted as $K_n$, the complete graph on $n$ vertices. Note that then a clique of size $k$ is an induced copy of a $K_k$. The graph $G$ is called bipartite if $V=A\dot{\cup} B$ for two disjoint stable sets $A$ and $B$. The complete bipartite graph $K_{m,n}$ is a bipartite graph with $\vert A\vert =m$, $\vert B\vert =n$ and $E=\lbrace \lbrace a,b\rbrace :a\in A,b\in B\rbrace$.

An $u$-$v$\textit{-path} is a sequence of distinct vertices starting with $u$ and ending with $v$, such that there exists an edge between every two consecutive vertices. If $u=v$ but all other vertices are still distinct, the sequence is called a \textit{cycle}. A graph that does not contain a cycle is \textit{acyclic}. We say a graph $G=(V,E)$ is \textit{connected}, if there exist a $u$-$v$-path for every pair of vertices $u,v\in V$.
With the previous definition we can define a \textit{tree} $T$ as a connected and acyclic graph. A union of disjoint trees is called a \textit{forest}.

Additionally, we can group trees after their form. We denote a \textit{path} on $n>2$ vertices as $P_n$. A \textit{star} $K_{1,n}$ on $n+1$ vertices is a tree with one center vertex of degree $n$ and $n$ leafs, i.e. vertices in a tree of degree $1$. Then, we can define a \textit{broom} as a path with a star at one end and a \textit{caterpillar} as a path where each vertex in the path furthermore may have an arbitrary number of leafs as neighbors.

A \textit{subdivision} of a graph $G=(V,E)$ is a graph obtained by subdividing edges of $G$. A subdivision of an edge $e=(u,v)\in E$ creates a new vertex $w$ and replaces $e$ with two new edges $(u,w)$ and $(w,v)$ in $E$. Observe that a subdivision of a tree is still a tree.\\

For the sake of the completeness of this collection of definitions, I want to add a final one, since it is used to describe some trees already proven to be $\chi$-bounding. Again, let $G=(V,E)$ be a graph. The eccentricity of a vertex $v\in V$ is defined as $\displaystyle e(v)=\max_{u \in V}\lbrace dist(v,u)\rbrace$. Then, the radius $\displaystyle r= \min_{v\in V}\lbrace e(v)\rbrace$ of $G$ is the minimum number $r\in\N$, such that there exist a vertex $v\in V$ where the distance between $v$ and any other vertex $u\in V$ is at most $r$. We often name this vertex $v$ the root of the tree.